Cloud correction of humidity radiances with case-specific uncertainty estimate

### 2020-11-20 Article/ici_submm_cloudcorr.tex
AMT format for figure names

\title{Estimation of cloud-corrected microwave humidity radiances with associated uncertainties}

%\title{Cloud correction and uncertainty characterisation of operational microwave humidty channels}

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. These examples illustrate the predicted quantiles for three different cases. The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for $\ynfcs$. To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered(SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

@@

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/correlation.pdf} 
	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown). For such cases,  QRNN-all has slightly better accuracy than QRNN-single.   The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single. Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.

@@

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K. For each quantile, the sample variation is also shown as box plot. }
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI). For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

@@

\subsection{Prediction accuracy}
\subsubsection{ICI}
%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
	\label{fig:error_distributions}	
\end{figure*}
\begin{table*}[t]
	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		%		\hline
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
		&&			   &			&	(All) & (5\,K) \\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

@@

\subsection{Prediction uncertainty}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
	\label{fig:calibration_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
	\label{fig:predicted_errors}	
\end{figure}

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

\section{QRNN network structure}
\label{appendix:hyperparamter}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
A high performing QRNN model also requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable/, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation data. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. We use quantile loss and CRPS for evaluation of the model performance.

@@

@@

\authorcontribution{The study was conceptualised and supervised by PE. The analysis, validation and visualisation of results was done IK. The QRNN package is made available by SP. IK wrote the original draft, with contributions from PE, SP and DID. DID also provided the data for MWHS-2. All authors contributed to the study with discussions and feedback.}

@@

\begin{acknowledgements}
The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19). David Duncan is supported by the EUMETSAT Fellowship Programme.
This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python and PyTorch).
\end{acknowledgements}

>>>>

\title{Cloud correction of humidity radiances with case-specific uncertainty 
	estimate}

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/fig01.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. These examples illustrate the predicted quantiles for three different cases. The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most applications only a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we chose the posterior median as the best estimate for $\ynfcs$. To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered(SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

@@

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/fig04.pdf} 
	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown). For such cases,  QRNN-all has slightly better accuracy than QRNN-single.   The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single. Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.

@@

\subsection{Prediction uncertainty}
\label{sec:uncertainty_mwhs}
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig05.pdf}	
	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. 1500 randomly selected cases are shown. The quantiles have been plotted at equidistant points. The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K. For each quantile, the sample variation is also shown as box plot. }
	\label{fig:prediction_uncertainty_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI). For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown. }
	\label{fig:calibration_mwhs}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/fig07.pdf}	
	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14. The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
	\label{fig:predicted_errors_mwhs}	
\end{figure}

@@

\subsection{Prediction accuracy}
\subsubsection{ICI}
%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig08.pdf} 
	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
	\label{fig:error_distributions}	
\end{figure*}
\begin{table*}[t]
	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
		\cline{3-6}
		%		\hline
		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
		&&			   &			&	(All) & (5\,K) \\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

@@

\subsection{Prediction uncertainty}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig09.pdf}	
	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/fig10.pdf}	
	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
	\label{fig:calibration_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/fig11.pdf}	
	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
	\label{fig:predicted_errors}	
\end{figure}

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

\section{QRNN network structure}
\label{appendix:hyperparamter}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/figB1.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
A high performing QRNN model also requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable/, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation data. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. We use quantile loss and CRPS for evaluation of the model performance.

@@

\begin{table*}[t]
	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rr|rr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN All sub-mm}&\multicolumn{2}{c}{QRNN only 325 GHz} \\
		\cline{3-8}
		%		\hline
		&&Clear-sky &   All-sky &  \multicolumn{2}{c|}{Predicted}&  \multicolumn{2}{c}{Predicted}   \\
		&&			   &			&	(All) & (5\,K) &	(All) & (5\,K)\\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%) & -0.03 & -0.01(6.2\%) \\
		&MAE       		&  0.64 &  2.32 &  0.70 &  0.60  &   0.73 &  0.61 \\
		&STD       		&  0.80 &  8.84 &  1.06 &  0.79  &  1.14 &  0.81 \\
		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  & -1.26 & -0.70\\
		\middlehline
		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%) & -0.03 & -0.01(3.6\%)  \\
		&MAE       		& 0.64 &   1.53 &  0.57 &  0.51 &  0.62 &  0.54\\
		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 &  0.99 &  0.70\\
		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22 & -2.67 & -0.38 \\
		\middlehline	
		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)&  0.02 &  0.03(2.2\%)  \\
		&MAE       		& 0.64 &   1.15 &  0.54 &  0.50  &  0.60 &  0.55\\
		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  &  0.94 &  0.70\\
		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  & -3.28 & -0.22\\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

@@

\authorcontribution{The study was conceptualised and supervised by PE. The analysis, validation and visualisation of results was done by IK. The QRNN package is made available by SP. ARTS bulk simulations were set up by SP, and MWHS-2 data was provided by DID. IK wrote the original draft, with contributions from PE, SP and DID. All authors contributed to the study with discussions and feedback.}

@@

\begin{acknowledgements}
The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19). David Duncan is supported by the EUMETSAT Fellowship Programme.
This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python, PyTorch, Numpy and Matplotlib).
\end{acknowledgements}
